\textbf{Supplementary materials: Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}

### 2023-11-17 supplementary_BiSC_outdoor_AP.tex

%%% --- Authors --- %%%
\author[1, 2, 3]{Alan Domínguez}
\author[1, 3, 4]{Payam Dadvand}
\author[1]{Marta Cirach}
\author[1]{Bruno Raimbault}
\author[1]{Toni Galmes}
\author[1]{Karl Samuelsson}
\author[1, 2, 3]{Mark Nieuwenhuijsen}
\author[1, 2, 3]{Jordi Sunyer}
\author[1, 2, 3]{Xavier Basagaña}
\author[1, 3]{Ioar Rivas}

%%% --- Affiliations --- %%%
\affil[1]{Barcelona Institute for Global Health (ISGlobal), Barcelona, Spain.}
\affil[2]{Universitat Popmpeu Fabra (UPF), Barcelona, Spain.}
\affil[3]{CIBER Epidemiología y Salud Pública (CIBERESP), Madrid, Spain.}
\affil[4]{London School of Hygiene and Tropical Medicine ( LSHTM), London, UK.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Predictor variables}
\section{}

>>>>

%%% --- Authors --- %%%
\author{Alan Domínguez, Payam Dadvand, Marta Cirach, Bruno Raimbault, Toni Galmes, Karl Samuelsson, Mark Nieuwenhuijsen, Jordi Sunyer, Xavier Basagaña, Ioar Rivas}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Land Use Regression modelling details}

\subsection{Predictor variables}
\subsection{Performance metrics}

\section{Dispersion modelling details}

\subsection{Predictor variables}
\subsection{Performance metrics}
